---
title: "Getting Started with binomial"
author: "Lu Zhang"
date: "May 2, 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```



## Binomial Distribution

The package `binomial` is a small package that adopts 'Binomial Distribution',which is a theoretical probability model that we can use when calculating probabilities about the number of successes in a fixed number of random trials performed under identical conditions.

This package can help you calculate the probability of a given condition, visually dispaly the binomial probability distribution of a series of conditions and a summary of those critical measures of binomial distributions.

## Calculate the number of combinations in which k successes can occur in n trials

Function `bin_choose()` can calculate the number of combinations in which k successes can happen in n trials. 

```{r}
# For example, if we cant to calculate the number of combinations in which 2 successes can occur in 5 trials. 
 bin_choose(n = 5, k = 2)
```

Additionally, `bin_choose` can calculate not only a single situation at one time, but also situations of different success numbers with a fixed trial times simultaneously.

```{r}
# For example, we can compute the number of combinations in which 1 or 2 or 3 successes can occur in 5 trials respectively.
bin_choose(5, 1:3)
```


## Compute the probability of a particular situation

Function `bin_probability` can be used to calculate the probability of getting k successes in n trials with the success probability of x.

```{r}
# probability of getting 2 successes in 5 trials(assuming prob of success = 0.5)
bin_probability(success = 2, trials = 5, prob = 0.5)
```

## Display a table of binomial probability distribution 

Function `bin_distribution()` is able to return a table of the probability distribution with two inputs: `trials` (the number of trials) and `prob` (the probability of success). The output will be an object of class 'bindis' and 'data.frame'.

```{r}
# binomial probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5)
```

we can also use `plot` method for "bindis"" objects to graphs the probability histogram.

```{r}
plot(dis1)
```

## Compute and display cumulative probabilities 

Function `bin_cumulative()` can give a data frame with both the probability distribution and the cumulative probabilities: success in the first column, probability in the second column, and cumulative probability in the third column. The output will be an object of class 'bincum' and 'data.frame'.

```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
dis2
```

If you want more visualized information, you can use `plot` method which is designed for objects of class 'bincum' to plot a graph.

```{r}
plot(dis2)
```

## Compute and display critical measures of binomial distribution

Function `bin_variable` have two argument: `trials` and `prob`, it will return an object of class "binvar", this function will help check the validity of these two inputs.

```{r}
bin1 <- bin_variable(trials = 10, prob = 0.3)
```

`print()` method for "binvar" can nicely print out "binvar" objects.

```{r}
print(bin1)
```

`summary()` method for "binvar" can give a full summary description of the "binvar" object, including trials, prob, mean, variance, mode, skewness and kurtosis. The return list is a "summary.binvar" object.

```{r}
summary(bin1)
```

`print()` method for "summary.binvar" can nicely print out "summary.binvar" objects.

```{r}
print(bin1)
```

