---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

---

`"binomial"` is a minimal R pacakge that provides functions to calculate probabilities about the number of successes in a fixed number of random trials performed under identical conditions by adopting "Binomial Distribution" Model.

- `bin_choose()` calculates the number of combinations in which k successes can happen in n trials. 

- `bin_probability()` calculates the the probability of getting k successes in n trials with the fixed success probability.

- `bin_distribution()` is able to produce a "bindis" data frame of the probability distribution.

- `plot()` method for a "bindis" object to plot the probability distribution.

- `bin_cumulative()` can give a "bincum" data frame with both the probability distribution and the cumulative probabilities.

- `plot()` method for a "bincum" object to plot the cumulative probability distribution.

- `bin_variable()` can check the validity of inputs: "prob" and "trials" and return an object of class "binvar"

- `print()` method for "binvar" can nicely print out an "binvar" object.

- `summary()` method for "binvar" object generate a full summary description of an object "binvar", including trials, prob, mean, variance, mode, skewness, kurtosis.

- `print()` method for "summary.binvar" can nicely print out "summary.binvar" objects.

## Motivation

---

This package has been developed to conveniently use the "Binomial Distribution" to calculate the probability of certain situations.

## Installation

---
Install the development version from GitHub via the package "devtools":

```{r}
# development version from GitHub:
#install.packages("devtools") 

# install "binomial" (without vignettes)
#devtools::install_github("gastonstat/cointoss")

# install "cointoss" (with vignettes)
#devtools::install_github("gastonstat/cointoss", build_vignettes = TRUE)

```
## Usage
```{r}
library(binomial)

# The number of combinations in which 2 successes can occur in 5 trials
bin_choose(n = 5, k = 2)

# Probability of getting 2 successes in 5 trials(assuming prob of success = 0.5)
bin_probability(success = 2, trials = 5, prob = 0.5)

# Binomial probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5)

# Use `plot` method for "bindis"" objects to graphs the probability histogram
plot(dis1)

# Give a data frame with both the probability distribution and the cumulative probabilities
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
dis2

# Use plot() method for a "bincum" object to plot the cumulative probability distribution.
plot(dis2)

# Function bin_variable() will help check the validity of these two inputs.
bin1 <- bin_variable(trials = 10, prob = 0.3)

# print() method for "binvar" can nicely print out "binvar" objects.
print(bin1)

# summary() method for "binvar" can give a full summary description of the "binvar" object
summary(bin1)

# print() method for "summary.binvar" can nicely print out "summary.binvar" objects.
print(bin1)
```
